\sysfull

### 2017-08-10 paper/coalescing.tex
Covering Koen's comments

\sys dynamically {\em coalesces} consecutively executing tasks at run time. When two tasks are coalesced, the first of the two tasks does not commit its updates to protected memory locations when it reaches a \transition statement. Instead, execution immediately continues from the beginning of the second of the two tasks. At the end of the second of the two coalesced tasks, \sys commits the pages that were updated by either of the coalescing tasks. The purpose of coalescing is to better amortize the run time overhead of committing updated pages when a task ends. If consecutive tasks access the same pages of data, the pages accessed by both tasks only need to be committed only once for the coalesced task rather than twice, one time for each of the tasks executed individually.

\sys can coalesce an arbitrary number consecutive tasks. As more tasks coalesce, their collective commit overhead amortizes better, potentially improving performance. As more tasks coalesce, the amount of potentially {\em wasted work} also increases. If power fails during a long sequence of coalesced tasks the lack of an intervening commit requires execution to restart from the {\em first} task in the sequence, failing to preserve the progress of any of
the tasks in the long sequence. \sys moderates the risk of coalescing and capitalizes on its benefit by dynamically, \emph{adaptively} determining a coalescing factor that combines many tasks without suffering an excess of wasted work.

@@

\sys determines $C$ for a given operating based on the number of tasks completed during the last operational period. \sys begins execution in a coalesced task with an infinite $C$ value. With a continuous power supply, the system executes from the start with all tasks as coalesced tasks entirely avoiding the cost of committing state. On intermittent power, the system executes a sequence of tasks that is interrupted by a power failure. \sys explicitly tracks $S$, the number of tasks completed during the previous operating period. \sys assigns $C$ to be equal to half of the value of $S$. If more tasks in total are able to complete in an operating period, \sys attempts to coalesce more tasks during the next operating period. If fewer tasks complete, \sys attempts to coalesce fewer tasks during the next operating period. $S$ includes the count of both coalesced and committing tasks completed. If no committing task completes, i.e., execution does not make progress, \sys updates $S$ and attempts to coalesce fewer tasks during the next operating period.

@@

\noindent\textbf{Task Coalescing Illustration:} Figure~\ref{fig:coalescing_example} illustrates how \sys coalesces tasks. Figure~\ref{fig:coalescing_example}(a) shows a sequence of six tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. Figure~\ref{fig:coalescing_example}(b) shows the same sequence of tasks executing as coalesced groups of three tasks. Figure~\ref{fig:coalescing_example}(c) shows how \sys adapts the value of $C$ based on $S$. \sys executes 12 tasks in the first operating period, assigning $S$ to six. \sys completes only five of the six coalesced tasks in the next operating period and then power fails. \sys sets $S$ to two in the next operating period, coalescing pairs of tasks and successfully committing two pairs before power fails. Execution resumes at the start of the third pair of tasks with a coalescing factor of two. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.

>>>>

\sys dynamically {\em coalesces} consecutively executing tasks at run time. When two tasks are coalesced, the first of the two tasks does not commit its updates to protected memory locations when it reaches a \transition statement. Instead, execution immediately continues from the beginning of the second of the two tasks. At the end of the second of the two coalesced tasks, \sys commits the pages that were updated by either of the coalescing tasks. The purpose of coalescing is to better amortize the run time overhead of committing updated pages when a task ends. If consecutive tasks access the same pages of data, the pages accessed by both tasks only need to be committed once.

\sys can coalesce an arbitrary number of consecutive tasks. As more tasks coalesce, their collective commit overhead amortizes better, potentially improving performance. As more tasks coalesce, the amount of potentially {\em wasted work} also increases. If power fails during a long sequence of coalesced tasks the lack of an intervening commit requires execution to restart from the {\em first} task in the sequence, failing to preserve the progress of any of
the tasks in the long sequence. \sys moderates the risk of coalescing and capitalizes on its benefit by dynamically, \emph{adaptively} determining a coalescing factor that combines many tasks without suffering an excess of wasted work.

@@

\sys determines $C$ for a given operation based on the number of tasks completed during the last operational period. \sys begins execution in a coalesced task with an infinite $C$ value. With a continuous power supply, the system executes from the start with all tasks as coalesced tasks entirely avoiding the cost of committing state. On intermittent power, the system executes a sequence of tasks that is interrupted by a power failure. \sys explicitly tracks $S$, the number of tasks completed during the previous operating period. \sys assigns $C$ to be equal to half of the value of $S$. If more tasks in total are able to complete in an operating period, \sys attempts to coalesce more tasks during the next operating period. If fewer tasks complete, \sys attempts to coalesce fewer tasks during the next operating period. $S$ includes the count of both coalesced and committing tasks completed. If no committing task completes, i.e., execution does not make progress, \sys updates $S$ and attempts to coalesce fewer tasks during the next operating period.

@@

\noindent\textbf{Task Coalescing Illustration:} 
%
%Figure~\ref{fig:coalescing_example} illustrates how \sys coalesces tasks. Figure~\ref{fig:coalescing_example}(a) shows a sequence of six tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. Figure~\ref{fig:coalescing_example}(b) shows the same sequence of tasks executing as coalesced groups of three tasks. 
%
Figure~\ref{fig:coalescing_example} shows how \sys adapts the value of $C$ based on $S$. \sys executes 12 tasks in the first operating period, assigning $S$ to six. \sys completes only five of the six coalesced tasks in the next operating period and then power fails. \sys sets $S$ to two in the next operating period, coalescing pairs of tasks and successfully committing two pairs before power fails. Execution resumes at the start of the third pair of tasks with a coalescing factor of two. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.

### 2017-08-10 paper/evaluation.tex
Covering Koen's comments

We present the experimental results of \sys performance. We start with describing the hardware environment (Section~\ref{sec:results_hardware}) followed by the software environment (Section~\ref{sec:results_software}) and we concluded by the evaluation results (Section~\ref{sec:results_evaluation}).

@@

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp}, i.e. build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller, and TI's MSP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} (hardware type will be specified per experiment in Section~\ref{sec:results_evaluation}). WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet} with TI Code Composer Studio version X~\cite{}\todo{Report on CCS version}{Amjad}. FET was also used as a power supply in non-intermittent power experiment. To measure energy consumption of all benchmark applications (please refer to Section~\ref{sec:results_software}) Carnegie Mellon's EDB~\cite{edb} was used. In experiments involving wireless power, WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. RFID reader is controlled by a PC running Ubuntu 10.4 executing open source Python-based \emph{sllurp} library~\cite{sllrp_github} enabling low-level RFID reader control. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance controlled experiments, WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code completion measurements have been performed using Salea~\cite{saleae} digital logic analyzer.

We also had alternative setup where we used MSP-TS430RGZ48C launchpad for continuous power experiment. We used internal timer for measuring run time. For harvested energy, we used ThingMagic Astra-EX RFID reader with power level of 17.25-30dBm. We used EDB~\cite{edb} for run time measurement. Applications were cross compiled using GCC and Clang, so that we can use LLVM for \sys compiler.\todo{Report on LLVM version}{Brandon}

>>>>

We present the experimental results of \sys's performance. We start with describing the hardware environment (Section~\ref{sec:results_hardware}) followed by the software environment (Section~\ref{sec:results_software}) and we concluded by the evaluation results (Section~\ref{sec:results_evaluation}).

@@

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp} build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller. WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet} with TI Code Composer Studio version 7. FET was also used as a power supply in non-intermittent power experiment. To measure energy consumption of all benchmark applications (please refer to Section~\ref{sec:results_software}) Carnegie Mellon's EDB~\cite{edb} was used. In experiments involving wireless power, WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to the Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. The RFID reader is controlled by a PC running Ubuntu 10.4 executing open source Python-based \emph{sllurp} library~\cite{sllrp_github}. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance-controlled experiments, the WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code execution times have been measured using Salea~\cite{saleae} digital logic analyzer.

We also used an alternative setup where the MSP-TS430RGZ48C launchpad was for continuous power experiments. We used internal timer for measuring run time. For harvested energy, we used the ThingMagic Astra-EX RFID reader with power levels in the [17.25,30]\,dBm range. We used EDB~\cite{edb} for execution time measurement. Applications were cross-compiled using GCC and Clang, so that we can use LLVM for \sys compiler.\todo{Report on LLVM version}{Brandon}
